Stock enhancement undermines community stability

### 2022-02-04 rmd/manuscript.Rmd
edit: manuscript

There is increasing awareness that stock enhancement with captive-bred organisms brings ecological risks to wild populations. Still, we may underestimate the negative impact of stock enhancement because current schemes rarely consider the consequences for the whole ecological community. Here, we use theory and long-term data of Japanese stream fish communities to show that stock enhancement undermines community stability. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion. Consistent with this prediction, fish communities showed greater temporal fluctuations and reduced biodiversity in rivers with the intensive stocking of hatchery masu salmon - one of the most valuable freshwater resources in the region. Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.

@@

Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010]. Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010]. Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks (e.g., the accumulation of deleterious alleles) [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010]. In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018]. The widespread use of captive breeding is perhaps because of the "myth" that the demographic benefits of released individuals may exceed the associated risks.

Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement. Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999a; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012]. Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability. Evidence for this hypothesis is lacking, however.

Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999a]. Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

@@

We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios. These scenarios cover a range of ecological contexts, differing in the intrinsic growth of the enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, environmental stochasticity $\sigma_{\epsilon}$, and relative fitness $f_R$ (see **Materials and Methods**). Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$). We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.

@@

The destabilizing effect emerges because stock enhancement affects the balance of species interactions that underpins community stability. In theory, the stable coexistence requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a]. Under this condition, competing species can grow from small populations because dominant species undergo stronger intraspecific competition [@carrollNicheFitnessDifferences2011a]. Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999a] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$). However, stock enhancement is externally controlled, and the number of releases is not subject to density-dependent regulation. Therefore, released individuals impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (**Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see **Materials and Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential effects of climates and local abiotic factors.

@@

The past few decades have witnessed substantial efforts to unveil ecological consequences of captive breeding, and there is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. Despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012]. While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive across terrestrial and aquatic taxa because the destabilizing effect emerged across diverse simulated scenarios.

>>>>

The past decades have witnessed efforts to unveil ecological risks associated with massive releases of captive-bred individuals into the wild (stock enhancement). Still, we may underestimate the negative impact because current schemes rarely consider the consequences of stock enhancement for the whole ecological community. Here, we use theory and long-term data of Japanese stream fish communities to show that stock enhancement undermines community stability. Our theory predicted that stock enhancement destabilizes community dynamics by facilitating competitive exclusion. Consistent with this prediction, fish communities showed greater temporal fluctuations and reduced biodiversity in rivers with the intensive stocking of hatchery masu salmon - a major freshwater resource in the region. Our findings paint a bleak picture for stock enhancement, reinforcing the recurrent calls for alternative management strategies.

@@

Human demands for natural resources are ever-increasing, such that active interventions are critical to the sustainable management of fisheries, forestry, and wildlife [@laikreCompromisingGeneticDiversity2010]. Captive breeding is common to enhance wild populations of diverse plant and animal taxa [@snyderLimitationsCaptiveBreeding1996; @laikreCompromisingGeneticDiversity2010]. Although there is growing recognition that releases of captive-bred organisms (hereafter, "stock enhancement") entail ecological risks such as the accumulation of deleterious alleles [@arakiGeneticEffectsCaptive2007; @krkosekDecliningWildSalmon2007], this method is still pervasive in conservation [@snyderLimitationsCaptiveBreeding1996] and natural resource management [@laikreCompromisingGeneticDiversity2010]. In fisheries, for example, billions of hatchery individuals are released annually across the globe [@kitadaEconomicEcologicalGenetic2018]. The widespread use of captive breeding is perhaps because of the "myth" that the demographic benefits of released individuals may exceed the associated risks.

Current debates, however, overlook the fact that we have rarely assessed the community-wide impact of stock enhancement. Species are all embedded in the complex web of interacting organisms, and the stable coexistence of competing species through density-dependent feedback underpins the emergent stability of ecological communities [@tilmanEcologicalConsequencesChanges1999; @carrollNicheFitnessDifferences2011a; @loreauDoesFunctionalRedundancy2004]. Stock enhancement may disrupt the sensitive balance of species interactions because it introduces unnaturally high numbers of individuals into the wild [@weberInteractionsHatcheryWild2003; @careyNativeInvadersChallenges2012]. Hence, this form of species management may intervene in the ecological process that allows competing species to coexist, ultimately degrading the long-term community stability. Evidence for this hypothesis is lacking, however.

Here, we use a simple theory to show that stock enhancement undermines long-term community stability, which we define as the relative size of fluctuations in total community density over time [@tilmanEcologicalConsequencesChanges1999]. Our theory illuminates that stock enhancement interferes with the internal regulation process of self-sustainable communities, compromising the stabilizing mechanism emerging from species niche differences. The present study further demonstrates the relevance of this general theory to natural systems by showing its congruence with Japanese stream fish communities, where \~10 million hatchery masu salmon (*Oncorhynchus masou masou*) are released annually for fisheries, recreation, and conservation purposes [@kitadaLessonsJapanMarine2020].

@@

We ran `r n_sim` time steps of `r max(sim_result$n_rep)` independent communities (i.e., simulation replicates) under each of `r nrow(param_set)` simulation scenarios. These scenarios cover a range of ecological contexts, differing in the intrinsic growth of an enhanced species $r_1$, competition $\bar{\alpha}$, carrying capacity $K$, and relative fitness $f_R$ (see **Materials and Methods**). Using the last `r unique(sim_result$n_timestep)` time steps, we obtained the following summary statistics of the total community density $\sum_i^SN_i$ to examine the community-level response to stock enhancement: the coefficient of variation (CV), the number of species persist (defined as $N_i > 0.01$ at $t=1600$), the temporal mean ($\mu$), and the temporal SD ($\sigma$). We also calculated the temporal mean and SD for the enhanced ($N_1$) and unenhanced species ($\sum_{i,i \ne 1}^S N_i$) separately to infer underlying mechanisms.

@@

The destabilizing effect emerges because stock enhancement affects the balance of species interactions that underpins community stability. In theory, the stable coexistence requires a niche difference that is large enough to overcome the relative difference in intrinsic competitive ability [@carrollNicheFitnessDifferences2011a]. Under this condition, competing species can grow from small populations because dominant species undergo stronger intraspecific competition [@carrollNicheFitnessDifferences2011a]. Such coexistence favors stable temporal dynamics of species-rich communities [@tilmanEcologicalConsequencesChanges1999] because it gives rise to "overyielding" [@loreauDoesFunctionalRedundancy2004; @carrollNicheFitnessDifferences2011a], i.e., total community density of a multispecies community exceeds what would be expected in a single species community ($\sum_i^S N_i > K$). However, stock enhancement is externally controlled, and the number of releases is not subject to density-dependent regulation. Therefore, released individuals impose additional intra- and interspecific competition that interferes with the ecological process producing overyielding.

@@

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the stock enhancement of masu salmon (**Figure 1E**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (**Figure 1C, D**), a long-term program exists to monitor stream fish communities along with the official stocking records. The majority of stocking occurs in spring, after which salmon fry stay in freshwater for \~1 year and compete with wild individuals during growing seasons. Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` protected watersheds (see **Materials and Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of stock enhancement on community dynamics while accounting for potential effects of climates and local abiotic factors.

@@

There is a general agreement that the distinctive features of captive-bred individuals bring fitness disadvantages in the wild [@arakiHatcheryStockingHelp2010; @snyderLimitationsCaptiveBreeding1996]. However, despite the significant attention to the fate of captive-bred individuals, current schemes rarely consider the self-regulation process of biodiversity. Our results suggest that the ignorance of this critical process may erode the long-term persistence of the recipient community, likely impacting the provisioning of ecosystem services [@cardinaleBiodiversityLossIts2012]. While our empirical example is limited to stream fish communities, we anticipate that this phenomenon is pervasive across terrestrial and aquatic taxa because the destabilizing effect emerged across diverse simulated scenarios.

### 2022-02-04 rmd/supporting_info.Rmd
edit: manuscript

@@

```{=tex}
\begin{align}
N_{i,t+1} = N_{i,t}~exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
\end{align}
```
where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obeys an normal distribution $Normal(0, \sigma_{\epsilon}^2)$. We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:

@@

**Fish stocking.** The stocking of masu salmon began in the 1950s. Hatchery fish are released in spring (fry [age 0+] and smolt [age 1+] stages) and fall (juvenile stage [age 0+]). Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level. We assembled annual records of stock enhancement (the number of fish released) from 1999 to 2019 for each release stage.

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate upstream watershed polygons for each sampling site. We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth. Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

```{=tex}
\begin{align}
ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
\end{align}
```
where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$. The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$). This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007]. We used median estimates of fish density $n_{s,t}$ to calculate temporal CVs, means ($\mu$), and SDs ($\sigma$).

We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data. Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate. We summarized the reconstructed community dynamics in **Figures S7-S9**.

We used linear regression to quantify the impact of stock enhancement on community dynamics. Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites. Specifically, we developed the following linear regression model taking either CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.

@@

```{=tex}
\begin{align}
\left\{
\begin{aligned}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$. The site-level predictors include upstream watershed area, air temperature, precipitation, and forest land use. Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**). The watershed-specific intercept was related to watershed-level predictors as:

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the watershed-specific intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture. All predictors were standardized (mean = 0, SD = 1) before the analysis.

@@

For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community statistics (the mean densities and SDs of the whole community, enhanced species, and unhenaced species). To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable (parameter combination $n$):

@@

where $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.

@@

  table_legend <- paste0("Sensitivity analysis of the community simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are Spearman's correlation between stock enhancement and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],". Explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")

>>>>

## stocking data
source(here::here("code/data_fmt_stock.R"))

df_stock_stage <- df_stock %>% 
  group_by(release_stage) %>% 
  summarize(stock = sum(abundance)) %>% 
  mutate(ratio = stock / max(stock),
         prop = stock / sum(stock))

@@

```{=tex}
\begin{align}
N_{i,t+1} = N_{i,t}~exp\left[r_i \left(1-\frac{N_{i,t} + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i} \right) \right]exp(\epsilon_{i,t})
\end{align}
```
where $r_i$ is the intrinsic growth rate, $\alpha_{ij}$ the competition coefficient of species $j$ on $i$, $K_i$ the carrying capacity, and $\epsilon_{i,t}$ the species response to stochastic environmental fluctuations that obey an normal distribution $Normal(0, \sigma_{\epsilon}^2)$. We modified this formula to include the effects of stock enhancement on reproduction and competition as follows:

@@

**Fish stocking.** The stocking of masu salmon began in the 1950s. Hatchery fish are released in spring (fry and smolt stages) and fall (juvenile stage). Although the fish release occurs at multiple locations within a watershed, the stocking information is available only at the watershed level. For each release stage, we assembled annual records of stock enhancement (the number of fish released; 1999-2019) from annual investigations by Hokkaido National Research Institute and Salmon and Freshwater Fisheries Research Institute. During the study period, the majority of stocking took place in spring at a fry stage (fry : juvenile : smolt = `r pull(df_stock_stage, ratio)[1]` : `r op(pull(df_stock_stage, ratio)[2])` : `r op(pull(df_stock_stage, ratio)[3])`)

**Environmental data.** At each sampling site, we measured the following environmental variables as potential covariates: upstream watershed area (km^2^; a proxy for stream size), proportional land use in the upstream watershed (forest, urban, agriculture), local climates (annual mean air temperature [$^\circ C$] and cumulative precipitation [mm]), and ocean productivity (sea surface chlorophyll *a* concentration [mg m^-3^]). We used MERIT Hydro [@yamazakiMERITHydroHighresolution2019] to delineate the upstream watershed polygon for each sampling site. We estimated the proportion of forest, urban, and agriculture in each watershed polygon based on land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhornCopernicusGlobalLand2020]. Climate data at each sampling site were extracted from CHELSA version 1.2 [@kargerClimatologiesHighResolution2017; @kargerDataClimatologiesHigh2018]. We extracted annual data of chlorophyll *a* concentration (2002-2019; resolution, 4.6 km^2^) from OceanColor [@seawifsmissionpageNasaOceanBiology2019] as a proxy for ocean productivity and calculated the average value within the 30-km radius of each river mouth. We used the following R packages to perform geospatial analysis: *sf* [@pebesmaSimpleFeaturesStandardized2018]*, raster* [@hijmansRasterGeographicData2020]*, exactextractr* [@bastonExactextractrFastExtraction2020]*, stars* [@pebesmaStarsSpatiotemporalArrays2020]*, whitebox* [@lindsayWhiteboxGATCase2016]*.*

@@

```{=tex}
\begin{align}
ln~n_{s,t+1} = ln~r_{s} + ln~n_{s,t} + \epsilon_{s,t}^{state}
\end{align}
```
where $ln~r_{s}$ is the site-specific rate of change at site $s$, and $\epsilon_{s,t}^{state}$ is the process error that follows a normal distribution as $\epsilon_{s,t}^{state} \sim Normal(0, \sigma_{state,s}^2)$. The site-specific rate of change is random draws from a normal distribution $ln~r_s \sim Normal(\mu_r, \sigma_r^2)$, assuming that community dynamics across Hokkaido have a shared temporal trend to some degree (the degree of shared trend is controlled by the SD $\sigma_r$). This hierarchical structure allows for improved parameter estimates by partially sharing information across sites [@gelmanDataAnalysisUsing2007]. We used median estimates of fish density $n_{s,t}$ to calculate the temporal CV, mean ($\mu$), and SD ($\sigma$) for each site. We summarized the reconstructed community dynamics in **Figures S7-S9**.

We assessed the predictive performance of our model using the Bayesian p-value [@keryIntroductionWinBUGSEcologists2010], a value of which takes a range of 0-1 and indicates over- (\~0.0), under- (\~1.0), or suitable-fitting (\~0.5) to the data. Bayesian p-values for our state-space models ranged from `r op(min(df_bp$mean))` to `r op(max(df_bp$mean))`, indicating that our model specification is appropriate.

We used linear regression to quantify the impact of stock enhancement on community dynamics. Although our focus is stock enhancement, each model included climatic and local abiotic variables to account for important environmental differences among sites. Specifically, we developed the following linear regression model taking either the CV, species richness (the number of species present during the observation period), mean, or SD as a response variable $y_s$ with a normal or a Poisson distribution.

@@

```{=tex}
\begin{align}
\left\{
\begin{aligned}
\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for CV, mean, and SD}\\
ln~\mu_{y,s} &= \gamma_{0,w(s)} + \sum_k \gamma_kx_{k,s} &&\text{for species richness}
\end{aligned}
\right.
\end{align}
```
$\gamma_{0,w(s)}$ is the watershed-specific intercept ($w(s)$ refers to site $s$ nested within watershed $w$) and $\gamma_k (k > 0)$ are the regression coefficients of site-level predictors $x_k$. The site-level predictors include upstream watershed area (log-transformed), air temperature, precipitation, and forest land use. Urban and agricultural land use were omitted because of either a limited value range (**Figure S10**) or a strong correlation with forest land use (**Figure S11**). The watershed-specific intercept was related to watershed-level predictors as:

```{=tex}
\begin{align}
\gamma_{0,w} &\sim Normal(\mu_{\gamma,w},\sigma_{\gamma}^2)\\
\mu_{\gamma,w} &=\delta_0+\sum_k\delta_k z_{k,w}
\end{align}
```
$\delta_{0}$ is the global intercept and $\delta_k (k > 0)$ are the regression coefficients. The watershed-level predictors $z_{k,w}$ include the yearly stocking of masu salmon (fry + juvenile + smolt; averaged for1999-2019) and ocean productivity (chlorophyll *a* concentration; averaged for 2002-2019). Ocean productivity was included because the majority of the observed species use marine habitats at a certain life stage (i.e., diadromous). The parameter $\sigma_{\gamma}$ accounts for random variation among watersheds that the watershed-level predictors cannot capture. All predictors were standardized (mean = 0, SD = 1) before the analysis.

@@

For each parameter combination, we estimated Spearman's rank correlation $\xi$ between the number of releases $R$ and community dynamics, which indicate the effect of stock enhancement under a given ecological context. To examine influences of simulation parameters on $\xi$ (**Table S1**), we developed the following regression model taking $\xi$ as a response variable:

@@

where $\xi_n$ is Spearman's rank correlation for parameter combination $n$, and $\zeta_k$ ($k = 0-7$) are the intercept ($\zeta_0$) and regression coefficients ($\zeta_{1-7}$). Explanatory variables were standardized (mean = 0, SD = 1) to compare regression coefficients.

@@

  table_legend <- paste0("Sensitivity analysis of the community simulation. Parameter estimates of linear regression models (standard errors in parenthesis) are shown. Response variables are Spearman's rank correlation between stock enhancement and either temporal mean density ($\\mu$) or SD ($\\sigma$) of ", c_text[i],". Explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")
